Try Bayesian Survival Analysis using the JACC study data (Bayesian Survival Analysis presentations)

### 2020-01-12 ForReport20200114/HandOutEngBayes.Rmd
updated figure setting

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.margin = FALSE}
library(tidyverse)
ggSample %>% 
  filter(Iteration >= 500 & Parameter %in% c("beta[5]", "HR[5]", "AFT[5]")) %>% 
  ggs_traceplot()
```

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.margin = FALSE, fig.height=7, fig.width=6}
library(tidyverse)
ggSample %>% 
  filter(Iteration >= 500 & Parameter %in% c("beta[5]", "HR[5]", "AFT[5]")) %>% 
  ggs_traceplot()
```
